---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  echo = TRUE
)
```

# Hello, welcome! :smiley: :grin:

# forester package

<!-- badges: start -->
<!-- badges: end -->

The `forester` package constitutes a set of functions with mathematical and statistical methods traditionally used by forestry engineers to analyze forest inventory data.

## Installation

You can install the released version of `forester` from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("forester")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DeivisonSouza/forester")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(forester)
data("pinus")
SRS(x = pinus$Volume, A = 400000, a = 600, FP = F, DT = F)
```
